The Place of the Local Group in the Cosmic Web

### 2014-07-29 paper/main.tex
updated table with the numbers of pairs in different environments

\begin{table*}
\begin{center}
\begin{tabular}{lcccc}\hline\hline
Sample & Peak & Filament & Sheet & Void\\
       & $n$ (\%) & $n$ (\%) & $n$ (\%) & $n$ (\%) \\\hline
2$\sigma$ & 4 (8.7) & 24 (52.2) &  17 (36.7) & 1 (2.2)\\
3$\sigma$ & 10 (8.3) & 58 (48.3) & 47 (39.2) & 5 (4.2)\\  
General & 1312 (23.9) & 1472 (26.9) & 1769 (32.3) & 927 (16.9)\\\hline
\end{tabular}
\caption{
Number of pairs in the four different kinds of environmtns. In
parethesis the same number as a percentage of the
total population. 
\label{table:web_type}}
\end{center}
\end{table*}

>>>>

\begin{table*}
\begin{center}
\begin{tabular}{ccccc}\hline\hline
Sample & Peak & Filament & Sheet & Void\\
       & $n$ (\%) & $n$ (\%) & $n$ (\%) & $n$ (\%) \\\hline
2$\sigma$ & 4 (8.7) & 24 (52.2) &  17 (36.7) & 1 (2.2)\\
3$\sigma$ & 10 (8.3) & 58 (48.3) & 47 (39.2) & 5 (4.2)\\  
General ($12.1<\log_{10} M_{\rm h}/\Msun<12.3$)& 8 (1.4) & 334 (55.5) & 259
(43.0) & 1 (0.1)\\\hline\hline  
\end{tabular}
\caption{
Number of pairs in the four different kinds of environments. In
parethesis the same number as a percentage of the
total population. 
\label{table:web_type}}
\end{center}
\end{table*}
